Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Frame rate eq
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@7 db7c848b-7755-4df2-b763-8796797afa52

Equalizer are an addition to compound trees. They modify parameters of their
respective subtree at runtime to optimize one aspect of the decomposition.

@@

Predominantly used by DPlex to smooth output framerate

>>>>

Equalizer are an addition to compound trees. They modify parameters of their
respective subtree at runtime to optimize one aspect of the decomposition. Due
to their nature, they are transparent to application developers, but might have
application-accessible parameters to tune their behaviour.

@@

The framerate equalizer smoothens the output frame rate of a destination
channel by instructing the corresponding window to delay its buffer swap to a
minimum time between swaps. This is regularly used for time-multiplexed
decompostions, where source channels tend to drift and finish their rendering
not evenly distributed over time. This equalizer is however fully independent of
DPlex compounds, and may be used to smoothen irregular application rendering
algorithms.
